\setuppapersize[A4]
\setuplayout[backspace=2cm, topspace=1cm, header=1cm, bottomspace=1cm, footer=1cm, width=middle, height=middle]
\setupbodyfont[libertinus, 14pt]
\setuppagenumbering[location={footer,center}]

\starttext
\centerline {Task 2}
Sentences about GSU:
\startitemize[n, nowhite, after]
\item It was opened in 1969.
\item Our University combines traditional values with new approaches.
\item Our University offers modern facilities and many forms of training.
\item The University trains future teachers, lawyers, economists, managers,
psychologists, engineers, programmers and research workers.
\item Part-time students combine work and studies, poor guys.
\item The chief task of a student is to learn.
\item Attendance at all lectures, seminars and practical classes is
compulsory for all students.
\item The course of study lasts for four or five years.
\item At the end of each semester students take credit tests on
practical work and examinations on theory.
\item Students of the Faculty of Mathematics and Programming Technologies
study physics, higher mathematics, descriptive geometry and social sciences.
\item As well as academic success, the social scene is an important part
of life at the University.
\stopitemize

\centerline {Task 3}
I made up {\bold my} own sentences:
\startitemize[nowhite, after]
\item I joined a university a few years ago.
\item I was going to study computer sciense and system analysis.
Computer sciense is about computing machinery, and 
system analysis is about analyzing things.
\item I got a quater of a room in the hostel.
\item Dormitory offered modern facilities.
\item I had a freezer and a shower in my disposal.
\item Living there, I was trying to combine my study and a healthy social life.
\item But I didn't succed in my study, thus I didn't get a scholarship.
\stopitemize

\centerline {Task 4}
I figured out the tense-forms of these sentences:
\startitemize[n, nowhite]
\item It was opened in 1969 on the basis of the Pedagogical Institute.
Past Simple.
\item It was the second University in Belarus. Past Simple.
\item Part-time students combine work and studies. Present Simple.
\item Many students will receive scholarship. Future Simple.
\item Most of the students have passed their exams successfully.
Present Perfect.
\item As well as academic success, the social scene is an important part of
life at the University. Present Simple
\stopitemize
\stoptext
