\setuppapersize[A4]
\setuplayout[backspace=2cm, topspace=1cm, header=1cm, bottomspace=1cm, footer=1cm, width=middle, height=middle]
\setupbodyfont[libertinus, 14pt]
\setuppagenumbering[location={footer,center}]

\starttext
\centerline {Task 253}
Я рассказал --- Мне рассказали → I told --- I was told. \\
Я показал --- Мне показали → I showed --- I was shown. \\
Она привела --- Ее привели → She {\bf{}led} --- She was {\bf{}led}. [lead led led]\\
Мы спросили --- Нас спросили → We asked --- We were asked \\
Мы ответили --- Нам ответили → We answered --- We were answered \\
Мы послали --- Нас послали → We sent --- We were sent \\
Они дали --- Им дали → They gave --- They were given \\
Он помог --- Ему помогли → He helped --- He was helped \\
Он посоветовал --- Ему посоветовали → He advised --- He was advised \\
Он забыл --- Его забыли → He forgot --- He was forgotten \\
Он вспомнил --- Его вспомнили → He remembered/recalled --- He was recalled \\
Мы пригласили --- Нас пригласили → We invited --- We were invited \\
Мы поправили --- Нас поправили → We corrected --- We were corrected \\
Он вылечил --- Его вылечили → He cured --- He was cured \\
Он позвал --- Его позвали → He called --- He was called \\
\vfil


\centerline {Task 254}
Мне рассказали --- Мне рассказывают --- Мне расскажут \\
→ I was told --- I am told --- I will be told \\
Мне показали --- Мне показывают --- Мне покажут \\
→ I was shown --- I am shown --- I will be shown \\
Ее привели --- Ее приводят --- Ее приведут \\
→ She was brought --- She is brought --- She will be brought \\
Нас спросили --- Нас спрашивают --- Нас спросят \\
→ We were asked --- We are asked --- We will be asked \\
Нам ответили --- Нам отвечают --- Нам ответят \\
→ We were answered --- We are answered --- We will be answered \\
Нас послали --- Нас посылают --- Нас пошлют \\
→ We were sent --- We are sent --- We will be sent \\
Им дали --- Им дают --- Им дадут \\
→ They were given --- They are given --- They will be given \\
Ему помогли --- Ему помогают --- Ему помогут \\
→ He was helped --- He is helped --- He will be helped \\
\page


\centerline {Task 255}
1. Bread {\bf is eaten} every day.\\
2. The letter {\bf was received} yesterday.\\
3. Nick {\bf will be sent} to Moscow next week.\\
4. I {\bf was asked} at the lesson yesterday.\\
5. I {\bf was given} a very interesting book at the library last Friday.\\
6. Many houses {\bf are builded} in our town every year.\\
7. This work {\bf will be done} tomorrow.\\
8. This text {\bf was translated} at the last lesson.\\
9. These trees {\bf were planted} last autumn.\\
10. Many interesting games always {\bf are played} at our PT lessons.\\
11. This bone {\bf will be given} to my dog tomorrow.\\
12. We {\bf were invited} to a concert last Saturday.\\
13. My question {\bf was answered} yesterday.\\
14. Hockey {\bf is played} in winter.\\
15. Mushrooms {\bf are gathered} in autumn.\\
16. Many houses {\bf were burned} during the Great Fire of London.\\
17. His new book {\bf will be finished} next year.\\
18. Flowers {\bf are sold} in shops and in the streets.\\
19. St. Petersburg {\bf was founded} in 1703.\\
\page


\centerline{Education}
We don't need no thought control\\
No dark sarcasm in the classroom\\
\centerline{\bf University}
A long time ago, when I was young and beautiful,
I was a student of belarusian state university.
It was opened in 1919, therefore it is the oldest university in Belarus. \\
It has faculties of Biology, Geography and Geoinformatics, Journalism,
History, Mechanics and Mathematics, Applied Mathematics and Computer Science,
Radiophysics and Computer Technologies, Social and Cultural Communications,
Philosophy and Social Sciences, Physics, Philology, Chemistry, Economics, Law,
Pre-University Education, Advanced Training and Retraining, International
Relations and Military Faculty. \\
I was a student in the faculty of Mechanics and Mathematics.
I choosed this faculty, because I like math, and there is word "Mathematics"
in "faculty of Mechanics and Mathematics".

Study lasts for four years. Every year is divided into two semesters.
At the end of each semester students take credit tests on practical work and
examinations on theory. I didn't pass the credit tests, so I am no longer
a student of BSU. \\
When I was a student, I studyed higher mathematics, descriptive geometry,
calculus, business analysis, computetional mathematics and social sciences. \\

Many students receive scholarship that depends much on their grades.
I had a problem with scholarship: I was a bad student with bad grades,
therefore I didn't receive scholarship for a few months.

I was living in the dormitory, because the university is located in Minsk,
and I am a resident of Gomel. I was living in the room with three guys:
Victor, Ilia and Danya.
Victor was the most serious one, he was working as a programmer since birth.
Danya was the cleverest one, he had passed the [{\bf how this thing is called? CT?}]
with 380 points.
Ilia was the normal one. He was a simple human being like me. \\
Later Danya and Victor leaved the dorm, because they decided to rent an
apartment. Ilia and Me also leaved the dorm, because we were expelled from
the university.
\centerline{\bf My student routine}
At 8:45 --- get up and go to university.\\
From 9:00 to maybe 4PM I was attending lectures and the things that are not lectures.\\
At 4PM --- be in library and do homework.\\
At 6PM --- go to dorm.\\
At 6:10PM --- do something social.\\
At 12PM --- try to sleep.\\
At 12:21PM -- sleep!\\
\centerline{\bf END}
\stoptext
